### 2023-06-08 python_excel_ite.tex
starting packaging

\section{Submodule 2: The packaging notebooks}
\subsection{Notebook 4: Project packaging}
\subsection{Notebook 5: Documentation}

>>>>

\section{Submodule 2: The packaging notebooks}

The first submodule and its three notebooks are very much about the type of modeling typically done in a spreadsheet based course. In a spreadsheet base course, students learn numerous Excel functions and techniques in the process of building and exercising such models. Similarly, numerous Python techniques are scattered throughout the three modeling focused notebooks. Now we shift gears and move beyond what might be considered prototyping and into the realm of deployment.

\begin{quote}
	content...

In the first three notebooks, we've developed some Python approaches to
typical Excel ``what if?'' analyses. Along the way we explored some
slightly more advanced Python topics (for relative newcomers to Python)
such as:

\begin{itemize}
	\tightlist
	\item
	List comprehensions,
	\item
	Basic OO programming, creating our own classes and using things like
	\texttt{setattr} and \texttt{getattr},
	\item
	Leveraging scikit-learn's \texttt{ParameterGrid} class,
	\item
	Faceted plots using Seaborn and matplotlib,
	\item
	Tuple unpacking, zip, and itertools,
	\item
	Safely copying objects,
	\item
	Root finding with, and without, \texttt{scipy.optimize},
	\item
	Using \texttt{numpy.random} to generate random variates from various
	probability distributions,
	\item
	Using \texttt{scipy.stats} to compute probabilities and percentiles,
	\item
	Importing our \texttt{data\_table}, \texttt{goal\_seek} and
	\texttt{simulate} functions from a module.
\end{itemize}

Now that we've got a critical mass of "proof of concept" code, let's figure out how to structure our project and create a deployable package. In addition, let's rethink our OO design and add some much needed documentation to the code.
\end{quote}

Creating a deployable Python package is

\subsection{Notebook 4: Project packaging}
\subsection{Notebook 5: Documentation}
